---
title: "Gurpinder Singh"
author: "STAT 108"
date: "11/9/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The research questions is to infer if there is a connection between quality of school and home prices inside of California for the year 2021.

Load all the followin library
```{r eval = TRUE}
library(tidyverse)
library(stringr)
library(knitr)
library(skimr)
library(broom)
library(readr)
```
The following data tries to measure the quality of school. More specifically it takes into account the following variables: Absentness/Reason for absent, chronic Absentee, population, stability of student, suspension count, nation test results.
```{r eval = TRUE}
absentReason <- read.delim("data/schoolData/abreason2021.txt")
chronicAbsentee <- read.delim("data/schoolData/chrabs2021.txt")
cohort <- read.delim("data/schoolData/cohort2021.txt")
stabilityCount <- read.delim("data/schoolData/sr2021.txt")
suspeneded <- read.delim("data/schoolData/susp2021.txt")
test <- read.delim("data/schoolData/test/test.txt")

```
The response variable is housing price. 
```{r eval = TRUE}
housing <- read_csv("data/housingData/housing.csv")
```

```{r eval = TRUE}
absentReason <- absentReason %>% 
  mutate(Average.Days.Absent=round(as.numeric(absentReason$Average.Days.Absent), digits = 0))

cohort <- cohort %>% 
  mutate(Dropout..Rate.=round(as.numeric(cohort$Dropout..Rate.), digits = 0))

stabilityCount <-stabilityCount %>% 
  mutate(Non.Stability.Rate..percent.=round(as.numeric(stabilityCount$Non.Stability.Rate..percent.), digits = 0))

suspeneded <-suspeneded %>% 
  mutate(Suspension.Rate..Total.=as.numeric(suspeneded$Suspension.Rate..Total., digits = 0))
```
```{r eval = TRUE}
glimpse(test)
```


```{r eval = TRUE}
ggplot(data = absentReason, aes(x =Average.Days.Absent)) +
  geom_histogram() +
  labs(x ="Average Days Absent",
       y = "Number Of Average Days Absent", 
       title = "Average Days Absent Distribution")
ggplot(data = chronicAbsentee, aes(x =ChronicAbsenteeismRate)) +
  geom_histogram() +
  labs(x ="Chronic Days Absent",
       y = "Number Of Chronic Days Absent", 
       title = "Chronic Days Absent Distribution")

ggplot(data = cohort, aes(x =Dropout..Rate.)) +
  geom_histogram() +
  labs(x ="Dropout rate",
       y = "Number Of Observations with Dropout rate", 
       title = "Dropout Rate Distribution")

ggplot(data = stabilityCount, aes(x =Non.Stability.Rate..percent.)) +
  geom_histogram() +
  labs(x ="Non Stability percentage",
       y = "Schools Non Stability Percentage Count", 
       title = "Non Stability Percentage Distribution")

ggplot(data = suspeneded, aes(x =Suspension.Rate..Total.)) +
  geom_histogram() +
  labs(x ="Suspeneded Percentage",
       y = "suspeneded Rate Count", 
       title = "Suspeneded Rate Distribution")
```