---
title: "Gurpinder Singh"
author: "STAT 108"
date: "11/9/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load all the followin library
```{r eval = TRUE}
library(tidyverse)
library(stringr)
library(knitr)
library(skimr)
library(broom)
library(readr)
```


```{r eval = TRUE}
airbnb <- read_csv("raw_data/listings.csv")
glimpse(airbnb)
spec(airbnb)
```

Exercise 1: 
```{r eval = TRUE}
airbnb <- airbnb %>% 
  mutate(cleaning_fee = price*0.02)
```
Exercise 2
```{r eval = TRUE}
ggplot(data = airbnb, aes(x =cleaning_fee)) +
  geom_histogram() +
  labs(x ="Cleaning Fee",
       y = "Number Of fees Collected", 
       title = "Cleaning Fee Distribution")

airbnb %>%
  summarise(max = max(cleaning_fee),
            min = min(cleaning_fee),
            mean = mean(cleaning_fee),
            med = median(cleaning_fee),
            sd = sd(cleaning_fee),
            iqr = IQR(cleaning_fee))
```
The following distribution shows a distribution with a right tail. Most values are between 0 to 25 with a mean of 6.5
Exercise 3
```{r eval = TRUE}
count(airbnb, neighbourhood)
```
The following shows 5 different neighborhoods and more over it shows Unincorporated Areas, City of Santa, City of Capitola are the most  observation
they make up 97.48002459 percent of the observations
Exercise 4
```{r eval = TRUE}
combinedData <- airbnb %>%
  mutate(neigh_simp = 
           fct_lump_n(neighbourhood, 
                      n=3,  
                      other_level = "Other"))
```
Exercise 5

```{r eval = TRUE}
count(combinedData,minimum_nights)
combinedData <- combinedData %>%
  filter(minimum_nights<= 3)
count(combinedData,minimum_nights)
```
The four most common values for the variable minimmum nights is 1,2,3,30
The value 30 stands out as there is a drastic jump in observations at 30 days which is one month exactly. The likely purpose is to take into account that the price will be different if they set minimum nights to 1 vs 14 since they want to give better deal for 14.
Exercise 6:
```{r eval = TRUE}
combinedData <- combinedData %>% 
  mutate(price_3_nights = price*3 + cleaning_fee)
```
Exercise 7:
```{r eval = TRUE}
reg_model <- lm(price_3_nights ~ neigh_simp +number_of_reviews+ reviews_per_month, data = combinedData)
  tidy(reg_model, conf.int = TRUE) %>% # output model
  kable(digits = 3) # format model output
coef(reg_model)

```
Exercise 8:
The coeffienient which indicates the number the price will decrease or increase per review given on the airbnb rating. In this case it is .335 The confidence interval indicates that the magnitude decrease/increase of price per review will lie between -.667 and .004 with 95 percent confidence

Exercise 9:

Exercise 10:
intercept indicates given neigh_simp ,number_of_reviews, and reviews_per_month are all zero the price for the airbnb will be predicted to be 1488.215	